A real-time particle filter for bus arrival prediction with discrete CDFs for journey planning

### 2020-10-11 new2020/main.Rnw
Add main pf results
Load texalpha package for characters in bib
texTalpha pkg
Try find the bug
Remove tables fix (rss)

@@

\usepackage{amsmath}
\usepackage{cleveref}

@@

@@

<<include-sections,echo=FALSE,results="asis">>=
for (file in list.files('sections', pattern = "*.tex", full.names = TRUE)) {
  cat(sprintf("\\input{%s}", file), "\n")
}
@

>>>>

%%%% FIX FOR TABLES
% \usepackage{etoolbox}

% \makeatletter
% \patchcmd{\@makecaption}
%   {\parbox}
%   {\advance\@tempdima-\fontdimen2\font\parbox} % decrease the width!
%   {}{}
% \makeatother
%%%% END FIX

@@

\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{longtable}
\usepackage{booktabs}

@@

\graphicspath{{sections/}}

@@

<<include-sections,echo=FALSE,results="asis">>=
for (file in list.files('sections', pattern = "*.tex$", full.names = TRUE)) {
  cat(sprintf("\\input{%s}", file), "\n")
}
@
